Predicting sales of newly published books

### 2015-08-19 paper.tex
un detalle en las tablas de datos: RAE y RRSE son porcentajes
completada la sección de Conclusiones

%% Many companies must face, as one of the most difficult tasks to
%% accomplish, new product sales estimation, since in many cases no
%% historical data to serve as guide is available. 
%% Moreover, some of them lack the knowledge about forecasting methods
%% and they can only make decisions based on the expert sales
  %% managers. 
% Eliminado esto.
When a new book is published the publishing house faces the problem of
how many books should be printed. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. That is
why in this paper we are tackling the problem or predicting sales to 
print the right amount of books, doing so even before the book has
reached shelves, which is when printing occurs. 
%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% In the literature, different methods of sales prediction, mainly for
% the fashion industry are proposed. 
% Esto no pega nada en el abstract - JJ
%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
%In this paper, a rule-based decision method is proposed to address the
%problem of predicting the publishing roll.  
% It's not proposed. It just obtained the best result with WEKA. - JJ 
% Publishing roll? ¿Qué es? - JJ
In this paper, which works with data on published books for several years in 
Spain, we first apply a data visualization and preprocessing strategy to find
out what are the relevant variables in the prediction of sales, and
then use standard data mining software to predict sales, and from them
deduce print roll, based on those variables. Our work discovers which
are the most relevant variables when predicting sales, and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishing houses,
since the obtained models provide information on the decision process and
does not require human intervention either for the operation or for
interpretation.
\end{abstract}

@@

In the field of publishing industry, the challenge is to print an
adequate number of copies but not too much, as the unsold volumes will
lead to losses, whereas if the number of printed copies was not
enough, you can always print more. 
Thus, it is extremely important using predictive tools to optimize 
production and improve the publishing company profits or minimize losses \cite{Zhao2001}
by forecasting the sales a new book might achieve. 
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole publishing roll.  
% [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...

@@

With this in mind, i this paper a data visualization and preprocessing strategy 
to find out what are the relevant variables describing a book in the prediction 
of book sales is proposed; then several standard data mining models 
for sales forecasting are evaluated so a publishing company 
can deduce and optimize print roll.

@@

Taking into account the kind of problem we address in this paper, 
a new product sales prediction for which no historical data is available,
the classical forecasting methods based on time series are not adequate. 
Thus, in this paper the relevant variables in the prediction of sales are determined
using data visualization tools and then, standard data mining software 
to predict sales is used to deduce print roll.
In addition, since publishers need models to explain obtained predictions, 
black box forecasting methods may not be suitable for this problem, so 
models based on rules are tested as an alternative.

@@

\textbf{FALTA EXPLICAR EN UN PAR DE PÁRRAFOS QUÉ ES EL SOM DE KOHONEN.} 
This method is usually applied to analyze data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those regions (clusters) 
with high training sample concentration and fewer where the samples are scarce.

@@

  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
Obtained results using the different forecasting methods on the dataset with 13 
variables per book can be shown in Table \ref{tabla:results13}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	  & MAE 			& RMSE 		& RAE 		& RRSE 		\\
\hline
  MP5 		& 2.94 $\pm$ 0.51 	& 65.49 	& 133.73 	& 11.10 	& 9.17 	  \\
\hline
  LR 		  & 0.33 $\pm$ 0.07 	& 100.813 & 257.63 	& 17.09 	& 17.67 	\\
\hline
  SVM 		& 49.10 $\pm$ 8.05	& 52.30	  & 139.45	& 8.87    & 9.56  	\\
\hline
  KNN 		& 0.03 $\pm$ 0.01 	& 198.16 	& 542.93 	& 33.59 	& 37.24 	\\
\hline
  MLP 		& 12.70 $\pm$ 3.08 	& 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN los de MLP
Obtained results using the different forecasting methods on the dataset with 7 
variables per book can be shown in Table \ref{tabla:results7}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)     & MAE       & RMSE    & RAE     & RRSE      \\
\hline
  MP5     & 7.39 $\pm$ 1.75   & 117.78   & 260.05  & 18.51   & 17.00  \\
\hline
  LR      & 40.59 $\pm$ 12.94 & 120.29  & 252.91  & 18.91   & 16.54   \\
\hline
  SVM     & 1547.91 $\pm$ 365.55 & 109.30  & 251.16   & 17.18     & 16.42   \\
\hline
  KNN     & 0.02 $\pm$ 0.01   & 293.98  & 1071.52  & 46.21   & 70.06   \\
\hline
  MLP     & 3265.71 $\pm$ 813.37   & 992.97 $\pm$ 0   & 1755.62 $\pm$ 0  & 156.07 $\pm$ 0   & 114.79 $\pm$ 0   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7}
\end{table*}

@@

La predicción de ventas en la industria editorial es un problema muy challenging durante los últimos años.

Para resolver este problmea, diferentes técnicas de datamining pueden ser muy útiles, al no haber datos históricos disponibles de las ventas.

La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
En este sentido, los árboles de decisión resultaron ser un modelo muy adecuado debido a la facilidad para explicar cómo se obtiene dicha predicción a partir de las variables descriptivas del nuevo libro. Esto, frente a los modelos tipo black-box como las ANN fue determinante desde el punto de vista de las necesidades de los expertos y la empresa.

@@

Como trabajos futuros sería interesante comparar las predicciones de los modelos obtenidos con otros basados en métodos de soft-computing, como genetic programming o fuzzy logic.

Por otro lado, puesto que hay algunas características que pueden afectar a la venta de productos de forma significativa, otra forma de mejorar las predicciones de ventas podría ser realizar un estudio en profundidad del efecto de la aplicación de descuentos y promociones.

>>>>

%% Many companies must face, as one of the most difficult tasks to
%% accomplish, new product sales estimation, since in many cases no
%% historical data to serve as guide is available. 
%% Moreover, some of them lack the knowledge about forecasting methods
%% and they can only make decisions based on the expert sales
  %% managers. 
% Eliminado esto.
When a new book is published the publishing house faces the problem of
how many books should be printed. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. That is
why in this paper we are tackling the problem or predicting sales to 
print the right amount of books, doing so even before the book has
reached shelves, which is when printing occurs. 
%Thus, making inaccurate predictions may lead to erroneous decisions that result in excess production that will not be sold, or even to a production deficit.
%That is the publishing roll problem, in which publishing companies must estimate the number of volumes printed, taking care not to print more than they actually end up selling. Thus, an automatic prediction of book sales to estimate the publishing roll would be helpful for publishers.
% In the literature, different methods of sales prediction, mainly for
% the fashion industry are proposed. 
% Esto no pega nada en el abstract - JJ
%In these works, when sales are stable with a clear trend over time, the classical methods are a good choice. 
%However, in the case of new products, such as a new book publishing, classical methods do not work properly.
%In this paper, a rule-based decision method is proposed to address the
%problem of predicting the publishing roll.  
% It's not proposed. It just obtained the best result with WEKA. - JJ 
% Publishing roll? ¿Qué es? - JJ
%[Pedro] en la traducción de términos Antonio propone traducirlo como "print run". Lo pongo así.
In this paper, which works with data on published books for several years in 
Spain, we first apply a data visualization and preprocessing strategy to find
out what are the relevant variables in the prediction of sales, and
then use standard data mining software to predict sales, and from them
deduce print-run, based on those variables. Our work discovers which
are the most relevant variables when predicting sales, and is
eventually able to predict sales with remarkable accuracy. In fact,
this method has been validated by the company that provided the data 
and incorporated in a business intelligence tool for publishing houses,
since the obtained models provide information on the decision process and
does not require human intervention either for the operation or for
interpretation.
\end{abstract}

@@

In the field of publishing industry, the challenge is to print an
adequate number of copies but not too much, as the unsold volumes will
lead to losses, whereas if the number of printed copies was not
enough, you can always print more. 
Thus, it is extremely important using predictive tools to optimize 
production and improve the publishing company profits or minimize losses \cite{Zhao2001}
by forecasting the sales a new book might achieve. 
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. %publishing roll.  
% [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...
% Antonio propone traducirlo como "print run". Lo pongo así.

@@

With this in mind, in this paper a data visualization and preprocessing strategy 
to find out what are the relevant variables describing a book in the prediction 
of book sales is proposed; then several standard data mining models 
for sales forecasting are evaluated so a publishing company 
can deduce and optimize print-run.

@@

Taking into account the kind of problem we address in this paper, 
a new product sales prediction for which no historical data is available,
the classical forecasting methods based on time series are not adequate. 
Thus, in this paper the relevant variables in the prediction of sales are determined
using data visualization tools and then, standard data mining software 
to predict sales is used to deduce print-run.
In addition, since publishers need models to explain obtained predictions, 
black box forecasting methods may not be suitable for this problem, so 
models based on rules are tested as an alternative.

@@

\textbf{FALTA EXPLICAR EN UN PAR DE PÁRRAFOS QUÉ ES EL SOM DE KOHONEN.}

This method is usually applied to analyze data as similar items tend to be 
mapped close together, while those items dissimilar, are mapped apart.
Also, the SOM graph represents and highlight very clearly those regions (clusters) 
with high training sample concentration and fewer where the samples are scarce.

@@

  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
Obtained results using the different forecasting methods on the dataset with 13 
variables per book can be shown in Table \ref{tabla:results13}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	  & MAE 			& RMSE 		& RAE (\%)		& RRSE (\%) 		\\
\hline
  MP5 		& 2.94 $\pm$ 0.51 	& 65.49 	& 133.73 	& 11.10 	& 9.17 	  \\
\hline
  LR 		  & 0.33 $\pm$ 0.07 	& 100.813 & 257.63 	& 17.09 	& 17.67 	\\
\hline
  SVM 		& 49.10 $\pm$ 8.05	& 52.30	  & 139.45	& 8.87    & 9.56  	\\
\hline
  KNN 		& 0.03 $\pm$ 0.01 	& 198.16 	& 542.93 	& 33.59 	& 37.24 	\\
\hline
  MLP 		& 12.70 $\pm$ 3.08 	& 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
Obtained results using the different forecasting methods on the dataset with 7 
variables per book can be shown in Table \ref{tabla:results7}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)     & MAE       & RMSE    & RAE (\%)     & RRSE (\%)      \\
\hline
  MP5     & 7.77 $\pm$ 1.15   & 117.78   & 260.05  & 18.51   & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41 & 120.29  & 252.91  & 18.91   & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50 & 109.30  & 251.16   & 17.18     & 16.42   \\
\hline
  KNN     & 0.03 $\pm$ 0.01   & 293.98  & 1071.52  & 46.21   & 70.06   \\
\hline
  MLP     & 3646.76 $\pm$ 64.83   & 705.69 $\pm$ 77.22   & 1608.69 $\pm$ 42.96  & 110.92 $\pm$ 12.14   & 105.18 $\pm$ 2.81   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7}
\end{table*}

@@

In this paper, the problem of how many books should be printed 
when a new book is published is faced using several data-mining and
forecasting methods.

This is a very challenging problem in this industry, because printing a higher 
number of volumnes than those finally sold will lead to losses, 
while printing an adequate number of copies will optimize sales and company earnings.
In addition, there are several difficulties inherent to the new book sales forecasting, 
such as dealing with limited data, finding adequate forecasting methods, and 
selecting the best method to use.

%La investigación descrita en este trabajo se ha llevado a cabo conjuntamente con una empresa editorial que ha facilitado un conjunto de datos con los que trabajar, así como con la ayuda de un experto en ventas de este campo para validar los resultados obtenidos.
A data set consisting of 3159 books provided by the Spanish 
publishing company Trevenque Editorial has been used.

In this paper, a data visualization method has been used to find out what are 
the relevant variables describing a book in the prediction of book sales.
Then, several standard data mining models for sales forecasting have been used 
to forecast new book sales, and from them deduce print-run, based on those variables.

The most relevant variables when predicting sales have been determined, 
while unrelated or superfluous ones have been removed, 
and sales predictions have been obtained using five different forecasting 
standard methods.
Proposed method was validated by the company and incorporated in a business 
intelligence tool for publishing houses.

In this sense, the decision trees proved to be a suitable model because of the ease 
to explain how the prediction is obtained from the variables that describe the new book. 
This, compared to the black-box models such as the ANN was decisive from the point 
of view of the needs of experts and the company.

@@

As future work, it would be interesting comparing the obtained forecasting results 
with other methods based on soft-computing, such as genetic programming or fuzzy logic.

Furthermore, since there are some characteristics that may affect product sales 
significantly, another way to improve sales predictions could be making a thorough 
study of the effect of the application of discounts and promotions.
